Quality Definitions of Qualities

### 2019-10-08 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
added reliability

Reliability is a critical quality for scientific software, since the results of
computations are meaningless, if they are not dependable.  Reliability is
closely tied to verifiability, since the key quality to verify is reliability,
while the act of verification itself improves reliability.

>>>>

Reliability is a critical quality for scientific software, since the results of
computations are meaningless, if they are not dependable.  Reliability is
closely tied to verifiability, since the key quality to verify is reliability,
while the act of verification itself improves reliability.\\
Reliability models can be used to predict reliability of a software product. For example measuring Mean Time to Fail (MTTF) can be a good measure for reliability
